%-------------------------
% Resume in Latex
% Author : Yauheni Baltukha
% Based off of: https://github.com/baltuky/latex-cv
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ragged2e}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
%\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Yauheni Baltukha} \\ \vspace{1pt}
    \small \href{mailto:evgenii.boltuho@gmail.com}{\underline{evgenii.boltuho@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/baltuky}{\underline{linkedin.com/in/baltuky}} $|$
    \href{https://github.com/baltuky}{\underline{github.com/baltuky}}
\end{center}


%-----------SUMMARY-----------
\section{Summary}
\justify
With over a decade of experience as a software engineer, I have successfully contributed to both small and large-scale
companies. As a versatile engineer, my true passion lies in constructing robust and scalable systems,
specializing in the development of backend services and data pipelines.
My enthusiasm for problem-solving and the inherent joy I find in overcoming intricate engineering challenges fuel my
drive to build innovative solutions.

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior SWE}{Jun 2021 -- Present}
      {Spotify}{Stockholm}
      \resumeItemListStart
        \resumeItem{Spearheaded the design and implementation of critical fraud prevention and mitigation system components using Java and Scala.}
        \resumeItem{Conducted comprehensive and high-quality code reviews, fostering collaboration and knowledge-sharing among team members, resulting in enhanced code quality and faster project delivery.}
        \resumeItem{Assumed a leadership role in conducting technical interviews, assessing candidates' skills and expertise, and contributing to the growth and success of the engineering team.}
        \resumeItem{Proactively served as an on-call engineer, diligently maintaining system uptime and effectively mitigating incidents to ensure seamless operations.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior SWE}{Nov 2019 -- Mar 2021}
      {Lyft}{Minsk}
      \resumeItemListStart
        \resumeItem{Implemented multi-versioning Protobuf schema support for Apache Flink consumer applications.}
        \resumeItem{Designed and developed a CLI tool to efficiently manage data pipelines.}
        \resumeItem{Designed a service to materialize collected data into Presto tables.}
        \resumeItem{Orchestrated the deployment of Helm charts for Presto and Hive Metastore components.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Senior SWE}{Jul 2019 -- Nov 2019}
      {Juno}{Minsk}
      \resumeItemListStart
        \resumeItem{Designed and developed Flink's source/sink components for backing up Kafka data to a remote file system.}
        \resumeItem{Developed Flink's Kudu sink to provide integration with Kudu for efficient data writing.}
        \resumeItem{Utilized Apache Airflow pipelines to schedule periodic backups of Kudu databases.}
        \resumeItem{Implemented the Kudu Flink Catalog to facilitate data accessibility through Flink's Table API.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Senior SWE}{Nov 2015 -- May 2019}	
      {EPAM Systems}{Minsk}
      \resumeItemListStart
        \resumeItem{Designed and developed Scala-based batch/streaming Spark applications to process lithography data.}
        \resumeItem{Created Kibana dashboards for processing engineers to enhance manufacturing cycles.}
        \resumeItem{Collaborated closely with data analysts and process engineers to gather and analyze requirements.}
        \resumeItem{Mentored and guided junior and mid-level software engineers.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
     \resumeProjectHeading
          {\textbf{Data collection platform for events analytics} $|$ \emph{Scala, Flink, k8s, AWS, Presto}}{May 2020 -- Mar 2021}
          \resumeItemListStart
            \resumeItem{Designed and developed a system to consume and store analytics events.}
            \resumeItem{Explored different approaches for materializing data into Presto tables and managing Presto table schemas.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Data Analytics Platform} $|$ \emph{Scala, Spark, Kafka, ELK, AWS}}{Sep 2018 -- Mar 2019}
          \resumeItemListStart
            \resumeItem{Created Kibana dashboards to visualize lithography logs.}
            \resumeItem{Developed Spark batch/streaming applications to process lithography logs and load them into ElasticSearch.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Hotel loyalty system} $|$ \emph{Java, Oracle, Spring Framework, GWT}}{Nov 2015 -- Sep 2017}
          \resumeItemListStart
            \resumeItem{Designed and developed a service for processing and managing promo codes.}
            \resumeItem{Integrated GWT UI application with the server-side for efficient promo code management.}
            \resumeItem{Developed load tests using Gatling for performance testing.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Scala} \\
     \textbf{Technologies}{: Apache Spark, Apache Kafka, AWS, Apache Flink, Docker, K8s} \\
    }}
 \end{itemize}
 
 %-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Belarusian State University of Informatics and Radioelectronics }{Minsk, BY}
      {Bachelor}{Sep. 2013 -- Jun 2017}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}